Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2017-09-05 Ben_Manuscripts/Paper1/Outline.tex
Intro edited and comments addressed

  A clear picture of the nanoscopic LLC membrane structure, gained by building 
  a molecular model will provide evidence to answer existing and newly proposed
  questions.
%MRS: break this down into more hierarchy - there are 11 separate points.  Can they be grouped at all for clearer understanding? elucidate what the aspects are we need a clearer picture. 
  \begin{itemize}
    \item We will limit our initial studies to studying assemblies formed by Na-GA3C11
    \item We have also chosen to focus our initial efforts on the development of 
    a model of the Col\textsubscript{h} phase membrane.
    \item Compared to the H\textsubscript{II} phase, the Col\textsubscript{h}
    phase is a simpler starting point, due to the absence of water, and has
    equivalent experimental structural data.
%MRS: since the questions we answer in the paper have a lot to do with the structure of the membranes, somewhere relatively early in the paper we need to lay out the facts that 1) these membranes could be really good (I think you do establish this) 2) we really would need to know the structure better to really do useful things with these, and 3) MD is a very helpful way to gain more information about the structure, because of the limited range of experiments we can do with these systems. That is the main rationale, and it should be made clear fairly early in the introduction.  Very important to make your story absolutely as clear as possible.
    \item Despite having structural data, there is still information which 
    experiment cannot definitively answer
    \item The Col\textsubscript{h} phase is described as having pores made of
    disks or layers stacked on top of one another, each containing a set 
    number of monomers. A simple simulation study of a similar molecule 
%MRS: suggests isn't the right word, since that implies it may still be valid, which probably isn't correct.  I would probably say how simple that test was, since what they did had almost no chance of getting the right answer in the proper context. We thought they did something reasonable, but they really didn't. 
%suggests
suggested
    that there are 4 monomers in each disk~\cite{zhu_methacrylated_2006}. A 
    separate calculation based on the volume of the liquid crystal monomers proposes
    that there are seven monomers in each layer~\cite{resel_structural_2000}. 
    A molecular model has the best chance of directly answering this question.
%MRS: phrasing
    %\item Once we know the number of monomers in each layer, we still do not know how 
    Even if we knew the number of monomers in each layer, we still would not know how 
    monomers in each layer are positioned with respect to other layers. 
    \item A driving force of self assembly in this system is thought to be pi-pi
    stacking interactions between aromatic headgroups \cite{gazit_possible_2002}. 
    \item Gas phase ab initio studies of benzene dimers have shown a clear energetic
    advantage for parallel displaced and T-shaped pi-pi stacking conformations versus a
    sandwiched conformation ~\cite{sinnokrot_estimates_2002}.
    \item Substituted benzene rings exhibit an even stronger pi-pi stacking 
    attraction which favors the parallel displaced configuration in all cases
    except where the substitutions are extremely electron withdrawing
    \cite{waller_hybrid_2006,ringer_effect_2006}.
    \item While we might be able to provide answers to these questions using a 
    molecular model, there remains the possibility that there is more than one 
    metastable state associated with a given LLC system.
    \item We must be able to identify which states can be produced experimentally
    and what implications each state might have regarding transport properties.
  \end{itemize}

  A molecular level understanding of LLC membrane structure will provide guidelines
  to reduce the large chemical space available to design monomers for creation of 
  separation-specific membranes.
  \begin{itemize}
%     \item LLCs are versatile and controllable with a \textbf{large chemical design
%     space} available for membrane design  %BJC: redundant
    \item  We do not yet understand how to reduce the effective pore size or 
    how to tune the chemical environment in the nanopores for effective water
    desalination or small organic separations.
    \item Rejection studies show that this membrane can not perform separations of
    solutes less than 1.2 nm because the pores are too large \cite{zhou_supported_2005}.
    \item Over the past 20 years, LLC membrane studies have been limited primarily 
    to Na-GA3C11 with some characterization done after minor structural modifications
    \cite{resel_structural_2000}. 
    \item Optimization has been performed through trial and error. The only source of 
    predictive modeling has been macroscopic models which likely do not adequately describe 
    transport at these length scales. % BJC: Reference. I think it is just w.r.t. bicontinuous cubic
    \item It will be challenging to efficiently narrow down the design space in 
    a laboratory setting.
    \item A good molecular model should incorporate a detailed picture of the nanoscopic pore 
    structure which will be crucial to understanding the role of monomer structure in 
    membrane design.
    \item Choice of head group may play a role in the rejection of charged or uncharged solutes.
    \item Choice of counterion may influence the establishment of a Donnan potential 
    affecting the degree to which the membrane can exclude charged species.
    \item Moieties inside the pores may interact with neutral solutes, rejecting
    on the basis of shape and 
    %MRS: size pretty much is hydrodynamic radius
    %size, 
    interations with specific chemical groups
rather than just hydrodynamic radius.
    %MRS: isn't this next point just a restatement of what was said at the top?
    \item  An atomistic understanding of pore structure and its influence on transport 
    is necessary to identify performance bottle necks and direct design of future membranes. 
  \end{itemize}

  We must show that the developed molecular model is consistent with
  physical observations so that we can rely on conclusions drawn about % better word for trust?
  structural features characteristic of the system.
  \begin{itemize}
    %MRS: main finding shouldn't be the model, but the things learned from the model. New suggestion below.
    %\item This article will illustrate the development of a predictive molecular model 
    %and the steps taken to ensure it mimics the real system within the constraints 
    %inherent to MD.
    \item In this study, we build a significantly more realistic atomistic model of LLC membranes than has ever previously been done, and explore what new structural information can be gained and what structure hypotheses are supported by this model.

    %MRS: this is kind of understood -- rephrasing?
    %\item To understand how physically realistic the model is, validation by comparison
    to experiment is necessary. 
    \item We validate the model using as much experimental information as pissible.
    We are %primarily 
    most interested in reproducing the 
    conclusions about structure which have been made from X-ray diffraction (XRD) 
    experiments and in matching ionic conductivity measurements~\cite{feng_thin_2016}.
    %MRS: these are really supporting items to the above: put them indented.
    \item We have comparied simulated X-ray diffraction patterns to experiment in 
    order to match major features present in the 2D patterns.
    \item We calculated ionic conductivity using two agreeing methods.
    \item We examined the the influence of crosslinking on membrane structure.

    %\item We have created a model that can be used to probe the large design space
    available for membrane design
    \item The structure-building approach and analysis used in this paper can be readily extended to the H\textsubscript{II}
    phase and other similar LC systems.
  \end{itemize}

>>>>

  A molecular level understanding of LLC membrane structure, enabled by molecular
  dynamics simulations, will provide guidelines to reduce the large chemical space
  available to design monomers for creation of separation-specific membranes.
  \begin{itemize}
%     \item LLCs are versatile and controllable with a \textbf{large chemical design
%     space} available for membrane design  %BJC: redundant
    \item  We do not yet understand how to reduce the effective pore size or 
    how to tune the chemical environment in the nanopores for effective water
    desalination or small organic molecule separations.
    \item Rejection studies show that this membrane can not perform separations of
    solutes less than 1.2 nm because the pores are too large \cite{zhou_supported_2005}.
    \item Over the past 20 years, LLC membrane studies have been limited primarily 
    to Na-GA3C11 with some characterization done after minor structural modifications
    \cite{resel_structural_2000}. 
    \item Optimization has been performed through trial and error. The only source of 
    predictive modeling has been macroscopic models which likely do not adequately describe 
    transport at these length scales. % BJC: Reference. I think it is just w.r.t. bicontinuous cubic
    \item It will be challenging to efficiently narrow down the design space in 
    a laboratory setting.
    \item A good molecular model should incorporate a detailed picture of the nanoscopic pore 
    structure which will be crucial to understanding the role of monomer structure in 
    membrane design.
    \item Choice of head group may play a role in the rejection of charged or uncharged solutes.
    \item Choice of counterion may influence the establishment of a Donnan potential 
    affecting the degree to which the membrane can exclude charged species.
    \item Moieties inside the pores may interact with neutral solutes, rejecting
    on the basis of shape and 
    %MRS: size pretty much is hydrodynamic radius
    %size, 
    interactions with specific chemical groups
rather than just hydrodynamic radius.
    %MRS: isn't this next point just a restatement of what was said at the top?
    %BJC: yes, deleted
  \end{itemize}

  Our approach to constructing a general model will be based on the development of a
  model of a specific LLC membrane which has ample experimental characterization. %BJC: ample too much?
    \begin{itemize}
    \item We have chosen to focus on assemblies formed by Na-GA3C11
    \item We have also narrowed our scope to the development of 
    a model of the Col\textsubscript{h} phase membrane.
    \item Compared to the H\textsubscript{II} phase, the Col\textsubscript{h}
    phase is a simpler starting point, due to the absence of water, and has
    equivalent experimental structural data.
    \item Despite having structural data, there is still information which 
    experiment cannot definitively answer
    \end{itemize}

%BJC: the following just seems like filler now that I've reorganized
%   A clear picture of the nanoscopic LLC membrane structure, gained by building 
%   a molecular model will provide evidence to answer existing and newly proposed
%   questions.
%     \begin{itemize}
%     \item Despite having structural data, there is still information which 
%     experiment cannot definitively answer
%     \end{itemize}

%MRS: break this down into more hierarchy - there are 11 separate points.  Can they be grouped at all for clearer understanding? elucidate what the aspects are we need a clearer picture. 
%BJC: I moved the logic for choice of monomer to system to model to a separate paragraph (above this). I then moved the other three things I talk about into their own paragraphs to keep the ideas separate (following paragraphs).

%MRS: since the questions we answer in the paper have a lot to do with the structure of the membranes, somewhere relatively early in the paper we need to lay out the facts that 1) these membranes could be really good (I think you do establish this) 2) we really would need to know the structure better to really do useful things with these, and 3) MD is a very helpful way to gain more information about the structure, because of the limited range of experiments we can do with these systems. That is the main rationale, and it should be made clear fairly early in the introduction.  Very important to make your story absolutely as clear as possible.
%BJC: I moved and edited a paragraph that was originally later on to be 2 above this one. I think it does a better job addressing points 2 and 3. And now it addresses those points earlier in the intro (as early as it could go where I think it still makes sense in context)

  We do not know the number of monomers that constitute the layers which stack
  on top of each other to create pores.
  \begin{itemize}
%     \item The Col\textsubscript{h} phase is described as having pores made of
%     disks or layers stacked on top of one another, each containing a set 
%     number of monomers. 
    \item A simple simulation study of a similar molecule 
%MRS: suggests isn't the right word, since that implies it may still be valid, which probably isn't correct.  I would probably say how simple that test was, since what they did had almost no chance of getting the right answer in the proper context. We thought they did something reasonable, but they really didn't. 
%suggests
%BJC: Okay, added a little more to emphasize that what they did isn't really useful.
suggested
    that there are 4 monomers in each layer. Their estimation is based on a
    simulated system containing only 16 total monomers which likely does not sufficiently
    model the chemical environment present in the real system.~\cite{zhu_methacrylated_2006}. 
    \item A separate calculation based on the volume of the liquid crystal monomers proposes
    that there are seven monomers in each layer~\cite{resel_structural_2000}. 
    \item A molecular model has the best chance of directly answering this question.
  \end{itemize}
%MRS: phrasing
    %\item Once we know the number of monomers in each layer, we still do not know how

    Even if we knew the number of monomers in each layer, we still would not know how 
    monomers in each layer are positioned with respect to other layers. 
    \begin{itemize}
      \item A driving force of self assembly in this system is thought to be pi-pi
      stacking interactions between aromatic headgroups \cite{gazit_possible_2002}. 
      \item Gas phase ab initio studies of benzene dimers have shown a clear energetic
      advantage for parallel displaced and T-shaped pi-pi stacking conformations versus a
      sandwiched conformation ~\cite{sinnokrot_estimates_2002}.
      \item Substituted benzene rings exhibit an even stronger pi-pi stacking 
      attraction which favors the parallel displaced configuration in all cases
      except where the substitutions are extremely electron withdrawing
      \cite{waller_hybrid_2006,ringer_effect_2006}.
    \end{itemize}

%     \item While we might be able to provide answers to these questions using a 
%     molecular model, there remains the possibility that there is more than one 
%     metastable state associated with a given LLC system.

% BJC: Does it make sense to talk about metastable states? It was never really a goal to figure out other metastable states. 
  There remains the possibility that there is more than one metastable state 
  associated with a given LLC system.
  \begin{itemize}
    \item We must be able to identify which states can be produced experimentally
    and what implications each state might have regarding transport properties.
  \end{itemize}

  We must show that the developed molecular model is consistent with
  physical observations so that we can rely on conclusions drawn about
  structural features characteristic of the system.
  \begin{itemize}
    %MRS: main finding shouldn't be the model, but the things learned from the model. New suggestion below.
    %\item This article will illustrate the development of a predictive molecular model 
    %and the steps taken to ensure it mimics the real system within the constraints 
    %inherent to MD.
    \item In this study, we build a significantly more realistic atomistic model of LLC membranes 
    than has ever previously been done, and explore what new structural information can be gained
    and what structure hypotheses are supported by this model.

    %MRS: this is kind of understood -- rephrasing?
    %\item To understand how physically realistic the model is, validation by comparison
    %to experiment is necessary. 
    \item We validate the model using as much experimental information as possible.
    \item We are %primarily 
    most interested in reproducing the 
    conclusions about structure which have been made from X-ray diffraction (XRD) 
    experiments and in matching ionic conductivity measurements~\cite{feng_thin_2016}.
    \begin{itemize}
    %MRS: these are really supporting items to the above: put them indented.
	    \item We have comparied simulated X-ray diffraction patterns to experiment in 
	    order to match major features present in the 2D patterns.
	    \item We calculated ionic conductivity using two agreeing methods.
	    \item We examined the the influence of crosslinking on membrane structure.
    \end{itemize}
    %\item We have created a model that can be used to probe the large design space
    % available for membrane design
    \item The structure-building approach and analysis used in this paper can be readily extended
    to the H\textsubscript{II} phase and other similar LC systems.
  \end{itemize}
